Selection of a subpopulation with little structure

### 2017-09-01 reports/resampling_report.Rmd
legend for sampling scheme fig

### Nested subsampling scheme
To ensure that a potential bias due to population structure would be
represented by an increased standard error of the predictive abilities we
conceived a nested resampling scheme.
A first level of sampling was applied to each combination of `Material` (*i.e.*
"Hybrid" or "Inbred"), `Scenario` ("A" and "B" for inbred lines; "None" for
hybrids), `Extent` ("Core" if every predictor was available for all genotypes
and "Full for the entire set of genotypes") and `Core_Fraction`, representing
the share of core-set genotypes for which data on all predictors were assumed
to be available.
The notion of `Core_Fraction` may sound contradictory to the concept of "Core"
and "Full" sets of genotypes but note that for the variable `Core_Fraction` we
artificially removed information on a predictor for some genotypes to implore
the influence of genetic space-coverage through incomplete predictors on
predictive ability.
This random subsampling procedure was repeated 20 times and stored as
`Rnd_Level2`.

>>>>

### Nested subsampling scheme
```{r sampling-prediction-scheme, fig.show='hold', fig.cap="Prediction sampling scheme. ($\\textbf{a}$) Level 1 sampling scheme. During the first round of sampling, 70% of the genotypes were drawn at random (black symbols) and assigned to the training set (TRN) whereas phenotypes for the other 30% of genotypes (yellow symbols) were set to missing for this particular random sample. The random samples drawn at this level were subsequently denoted as s~1~ to s~20~. ($\\textbf{b}$) Level 2 sampling scheme. For maize inbred lines from the diversity panel, some genotypes had both genotypic and transcriptomic predictor data (black symbols). For each level of s from the first round of random sampling, a second round of random sub-sampling was applied where x% of the genotypes from the training set of s were declared to have both, genotypic and transcriptomic data (black symbols) whereas 1-x% of the genotypes were declared to have only genotypic information (gray symbols). This nested subsampling process was repeated 20 times and for nine different values of $x = (0.1, 0.2, 0.3, \\dots, 0.9)$. ($\\textbf{c}$) Leave-one-out cross-validation (LOOCV) scheme for maize diversity panel inbred lines. For each of the subsets from level 1 (and level 2) LOOCV was applied. Thereto, $n$ TST were generated (yellow symbols) where all genotypes eligible for TRN membership based on $\\textbf{a}$ were assigned to TRN (black symbols). ($\\textbf{d}$) LOOCV scheme for maize hybrids. This scheme is based solely on level 1 randomization in $\\textbf{a}$ and, for each level of s, places only T0 hybrids, which do not share a common parent with a TST hybrid, inside the TRN."}
knitr::include_graphics("compound_plot.svg", auto_pdf = FALSE)
```

To ensure that a potential bias due to population structure would be
represented by an increased standard error of the predictive abilities we
conceived a nested resampling scheme.
A first level of sampling was applied to each combination of `Material` (*i.e.*
"Hybrid" or "Inbred"), `Scenario` ("A" and "B" for inbred lines; "None" for
hybrids), `Extent` ("Core" if every predictor was available for all genotypes
and "Full for the entire set of genotypes") and `Core_Fraction`, representing
the share of core-set genotypes for which data on all predictors were assumed
to be available.
The notion of `Core_Fraction` may sound contradictory to the concept of "Core"
and "Full" sets of genotypes but note that for the variable `Core_Fraction` we
artificially removed information on a predictor for some genotypes to implore
the influence of genetic space-coverage through incomplete predictors on
predictive ability.
This random subsampling procedure was repeated 20 times and stored as
`Rnd_Level2`.
